### 2022-05-18 manuscript.Rmd
Add raw data as TSV

# Download spreadsheets from the literature search from Google Drive
excel_url <- "https://docs.google.com/spreadsheets/d/1xnC0NlQYTXavXaeqQidhi7UKb1pCGAl9Ry3h3Uz3mi0"
excel_file <- here(data_dir, "literature_search.xlsx")
# googledrive::drive_auth(use_oob = TRUE)
# googledrive::drive_download(excel_url, excel_file, overwrite = TRUE)

# Read the sheets
raw_screening <- read_excel(excel_file, sheet = "screening")
raw_meta <- read_excel(excel_file, sheet = "included", na = "NA")
raw_gender <- read_excel(excel_file, sheet = "gender_differences", na = "NA")

@@

    # Add unique experiment identifier
    experiment = str_c(year, article, group_long, sep = ", "),

@@

# Create forest plot
dat_meta %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment (row) per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals for each experiment
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian credible intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_meta,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_meta,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_meta$intercept),
      print_num(summ_meta$intercept.lower),
      print_num(summ_meta$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add column headers
  annotate(
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = descriptives$n_experiments + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = descriptives$n_experiments + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "2.5%",
      "97.5%"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, descriptives$n_experiments + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

@@

# Get an overview of the different effect sizes
dat_gender %>%
  select(
    article,
    group_long,
    gi,
    di,
    di_type,
    d,
    d_t,
    d_f,
    d_diff,
    sei
  ) %>%
  print(n = Inf)

@@

```{r, selection_process}
# Compute interrater agreement for binary decision (include vs. exclude)
(irr_bin_perc <- with(
  raw_screening, mean(bin_1 == bin_2)
))
(irr_bin_kappa <- with(
  raw_screening, psych::cohen.kappa(cbind(bin_1, bin_2))
))
irr_bin_kappa_w <- as.list(irr_bin_kappa$confid["weighted kappa", ])

# Compute interrater agreement for specific exclusion codes
(irr_code_perc <- with(
  raw_screening, mean(code_1 == code_2)
))
(irr_code_kappa <- with(
  raw_screening, psych::cohen.kappa(cbind(code_1, code_2))
))
irr_code_kappa_w <- as.list(irr_code_kappa$confid["weighted kappa", ])

>>>>

# Read the relevant spreadsheets
raw_screen <- read_tsv(here(data_dir, "02_screen.tsv"), na = "NA")
raw_meta <- read_tsv(here(data_dir, "03_meta.tsv"), na = "NA")
raw_gender <- read_tsv(here(data_dir, "04_gender.tsv"), na = "NA")

@@

    # Add unique experiment identifier
    experiment = str_c(year, article, group, sep = ", "),

@@

# Create forest plot
dat_meta %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment (row) per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals for each experiment
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian credible intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_meta,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_meta,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_meta$intercept),
      print_num(summ_meta$intercept.lower),
      print_num(summ_meta$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add column headers
  annotate(
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = descriptives$n_experiments + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = descriptives$n_experiments + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "2.5%",
      "97.5%"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, descriptives$n_experiments + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

@@

# Get an overview of the different effect sizes
dat_gender %>%
  select(
    article,
    group,
    gi,
    di,
    di_type,
    d,
    d_t,
    d_f,
    d_diff,
    sei
  ) %>%
  print(n = Inf)

@@

```{r, selection_process}
# Compute interrater agreement for binary decision (include vs. exclude)
(irr_bin_perc <- with(raw_screen, mean(bin_1 == bin_2)))
(irr_bin_kappa <- with(raw_screen, psych::cohen.kappa(cbind(bin_1, bin_2))))
irr_bin_kappa_w <- as.list(irr_bin_kappa$confid["weighted kappa", ])

# Compute interrater agreement for specific exclusion codes
(irr_code_perc <- with(raw_screen, mean(code_1 == code_2)))
(irr_code_kappa <- with(raw_screen, psych::cohen.kappa(cbind(code_1, code_2))))
irr_code_kappa_w <- as.list(irr_code_kappa$confid["weighted kappa", ])

### 2022-05-18 supplement.Rmd
Add raw data as TSV

```{r, tabs1, include=TRUE}
# Save table of experiments for the meta-analysis of rotation
dat_meta %>%
  mutate(
    age_mean = print_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = as.integer(sample_size),
    Females = as.integer(round(female_percent * sample_size)),
    `Age ($M$ ± $SD$)` = str_c(age_mean, "±", age_sd, sep = " "),
    Task = as.character(task),
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) %>%
  mutate(
    across(.fns = function(x) ifelse(is.na(x), "n/a", x))
  ) -> tabs1

@@

  # Re-fit the meta-analysis, leaving out one experiment at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat_meta)), function(jackknife_index) {
    dat_jackknife <- dat_meta[-jackknife_index, ]
    res_jackknife <- update(
      res_meta,
      newdata = dat_jackknife,
      seed = seed,
      refresh = 0
    )
    print_res_table(
      res_jackknife,
      label_1 = dat_meta$article[jackknife_index],
      label_2 = dat_meta$group_long[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Experiment"
    )
  }) %>%
    # Show article labels only for the first experiment (row) per article
    mutate(
      Article = if_else(Article == lag(Article, default = ""), "", Article),
    ) -> tabs3

@@

```{r, tabs4, include=TRUE}
# Read PRISMA checklist from file
tabs4 <- read_csv(
  here(data_dir, "prisma_checklist.csv"),
  col_types = "ccc", na = character()
)

@@

# Create forest plot
dat_gender %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment (row) per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian credible intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_gender,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_gender,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_gender$intercept),
      print_num(summ_gender$intercept.lower),
      print_num(summ_gender$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add column headers
  annotate(
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = nrow(dat_gender) + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = nrow(dat_gender) + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "2.5%",
      "97.5%"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, nrow(dat_gender) + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

>>>>

```{r, tabs1, include=TRUE}
# Save table of experiments for the meta-analysis of rotation
dat_meta %>%
  mutate(
    age_mean = print_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group,
    `Sample size` = as.integer(sample_size),
    Females = as.integer(round(female_percent * sample_size)),
    `Age ($M$ ± $SD$)` = str_c(age_mean, "±", age_sd, sep = " "),
    Task = as.character(task),
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = str_c(as.integer(stimuli_dimensions), "D")
  ) %>%
  mutate(
    across(.fns = function(x) ifelse(is.na(x), "n/a", x))
  ) -> tabs1

@@

  # Re-fit the meta-analysis, leaving out one experiment at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat_meta)), function(jackknife_index) {
    dat_jackknife <- dat_meta[-jackknife_index, ]
    res_jackknife <- update(
      res_meta,
      newdata = dat_jackknife,
      seed = seed,
      refresh = 0
    )
    print_res_table(
      res_jackknife,
      label_1 = dat_meta$article[jackknife_index],
      label_2 = dat_meta$group[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Experiment"
    )
  }) %>%
    # Show article labels only for the first experiment (row) per article
    mutate(
      Article = if_else(Article == lag(Article, default = ""), "", Article),
    ) -> tabs3

@@

```{r, tabs4, include=TRUE}
# Read PRISMA checklist from file
tabs4 <- read_tsv(here(data_dir, "05_prisma.tsv"), na = character())

@@

# Create forest plot
dat_gender %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment (row) per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian credible intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_gender,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_gender,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_gender$intercept),
      print_num(summ_gender$intercept.lower),
      print_num(summ_gender$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add column headers
  annotate(
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = nrow(dat_gender) + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = nrow(dat_gender) + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "2.5%",
      "97.5%"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, nrow(dat_gender) + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )
